Garbage Collection Evaluation Infrastructure for the Cog VM

### 2018-06-12 paper.tex
well, thats an intro

Firstly, we contacted multiple companies using the Cog VM in production on memory intensive application (>1Gb heaps) and built benchmarks out of their deployed application. As an example, we will discuss in the paper the Moose benchmarks implemented in collaboration with Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly release the model. This behavior was turned into three benchmarks, growing, accessing and shrinking the heap.

Secondly, \todo{Sophie :-) a few sentence on your bench}

- Gc algo ref

- We then evaluated the two reference algorithms on the infrastructure built to have reference benchmark results.

- related and futur

@@

\subsection{Moose benchmark}

@@

\subsection{Configurable benchmark}

>>>>

Firstly, we contacted multiple companies using the Cog VM in production on memory intensive application (>1Gb heaps) and built benchmarks out of their deployed application. As an example, we will discuss in the paper in Section \ref{sec:mooseBench} the Moose benchmarks implemented in collaboration with Feenk\footnote{https://feenk.com/}. Part of the business of Feenk consists in analysing software written in multiple programming languages using the open-source framework Moose~\cite{MoosePaper1,MooseBook1}. Using Moose, the application parses the software to analyse into a model, performs analysis on it and lastly release the model. This behavior was turned into three benchmarks, growing, accessing and shrinking the heap.

Secondly, \todo{Sophie :-) a few sentence on your bench + ref} \ref{sec:confBench}

To evaluate a new algorithm, we also need to compare it to reference implementations. The Cog VM features a Mark-Compact algorithm in production. The compaction phase is quite specific since it moves objects in memory and spend time updating references. In addition to this algorithm, we implemented a Mark-Sweep, which does not move objects in memory and is quicker to perform. Section \ref{sec:ref} details the two implementations.

We evaluated both algorithm on the benchmarks we built to provide results of the reference algorithms on the infrastructure built.

We conclude the paper by discussing some related work, the GC benchmarks suites for Java and the ACDC benchmarks, and some future work.

@@

\subsection{Moose benchmark}
\label{sec:mooseBench}

@@

\subsection{Configurable benchmark}
\label{sec:confBench}
